Appendix

### 2018-07-18 manuscript/appendix.Rmd
towards appendix cleanup

```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots"}
partition_splits <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)

@@

```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont"}
lg <- lagosne_load("1.087.1")
nes_nws_temp <- dplyr::left_join(nes_nws, select(lg$iws, lagoslakeid, iws_ha))
nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
                                       nes_nws_temp$p_pnt_source_septic,
                                       nes_nws_temp$p_pnt_source_industrial),
                                 na.rm = TRUE)
nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
us_states <- st_intersects(us_states(), nes_nws_sf)
us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]

@@

```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5.3, fig.cap="Exploratory plots cont x 2"}
lg <- lagosne_load("1.087.1")

@@

```{r stream_density-vs-link_length}
test <- dplyr::select(nes_nws, 
              avg_link_length, 
              stream_density, 
              closest_lake_distance) %>%
dplyr::rename("Average Link Length" = avg_link_length,
              "Stream Density" = stream_density,
              "Closest Lake Distance" = closest_lake_distance) %>%
dplyr::mutate(`Closest Lake Distance` = `Closest Lake Distance` / 100, 
              `Average Link Length` = `Average Link Length` / 100)

@@

```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# nws_lakes <- pull_lakes(nws)
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")
# saveRDS(nws_lakes, "../data/nws_lakes.rds")

@@

```{r best_partition_maps, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(tmap)
library(sf)
library(LAGOSNE)
library(USAboundaries)
library(dplyr)

@@

```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3, eval=FALSE}
plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
          title = "Link Length")
```

```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE}
results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
ll_split <- dplyr::filter(results_table, 
                          nws_names == "avg_link_length" & 
                          scale == "nws")$splits

>>>>

```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots", eval=FALSE}
partition_splits <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)

@@

```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont", eval=FALSE}
lg <- lagosne_load("1.087.1")
nes_nws_temp <- dplyr::left_join(nes_nws, select(lg$iws, lagoslakeid, iws_ha))
nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
                                       nes_nws_temp$p_pnt_source_septic,
                                       nes_nws_temp$p_pnt_source_industrial),
                                 na.rm = TRUE)
nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
us_states <- st_intersects(us_states(), nes_nws_sf)
us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]

@@

```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5.3, fig.cap="Exploratory plots cont x 2", eval=FALSE}
lg <- lagosne_load("1.087.1")

@@

```{r stream_density-vs-link_length, eval=FALSE}
test <- dplyr::select(nes_nws, 
              avg_link_length, 
              stream_density, 
              closest_lake_distance) %>%
dplyr::rename("Average Link Length" = avg_link_length,
              "Stream Density" = stream_density,
              "Closest Lake Distance" = closest_lake_distance) %>%
dplyr::mutate(`Closest Lake Distance` = `Closest Lake Distance` / 100, 
              `Average Link Length` = `Average Link Length` / 100)

@@

```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# nws_lakes <- pull_lakes(nws)
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")
# saveRDS(nws_lakes, "../data/nws_lakes.rds")

@@

```{r best_partition_maps, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
library(tmap)
library(sf)
library(LAGOSNE)
library(USAboundaries)
library(dplyr)

@@

```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3, eval=FALSE, eval=FALSE}
plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
          title = "Link Length")
```

```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE, eval=FALSE}
results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
ll_split <- dplyr::filter(results_table, 
                          nws_names == "avg_link_length" & 
                          scale == "nws")$splits
